[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
formating

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 
  dwplot(by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Pooled OLS") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

>>>>

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails

plot_pooled <- filter(df_plot, type == "Pooled OLS") %>% 
  dwplot(by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Pooled OLS") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
